Insert the article title here

### 2018-08-30 writeup/manuscript.tex
updated figures to remove title.

\begin{figure}
\centering
\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
\caption{Histograms showing the range of individual differences found in the ACVS task.}
\label{fig:acvs_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
\caption{What do we want this figure to actually be?}
\label{fig:foraging_summary}
\end{figure}

>>>>

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
\caption{Histograms showing the range of individual differences found in the ACVS task.}
\label{fig:acvs_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
\caption{Histogram of mean run lengths for (a) feature and (b) conjunction foraging tasks.}
\label{fig:foraging_summary}
\end{figure}
